---
title: "Love vs extraterrestials"
author: "Jacob Welsh"
date: "10 March 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

$H_0$ : No relation between the belief of love at first sight and belief in extra life.  
$H_A$ : There is a relation between love at first sight and extra life.

Graphic Display

```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab= 'love @ first sight')
```


People who belive in love at first sight also tend to believe in extraterrestrial life.  

Numerical Summary

```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```
    
It looks like those who believe in extra life also believe in love at first sight.


Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We reject the null, because the p-value shows no relation between the two beliefs.

# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?
  
$H_0$ : There is no difference between genders on belief in extra life.  
$H_A$ : There is a difference between the genders in belief on extra life.  
  
Graphical

```{r}
barchartGC(~sex + extra_life,data=mydata)
```

This barchart seems to show many more males believing in ET life.


Numerical

```{r}
table1 <- xtabs(~sex + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```

In this table the yes columns have higher numbers then no columns for males, and has more no than yes for females.

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The p-value in this inference shows .2, meaning we fail to reject the null hypo. There is a difference in genders on belief of extra life.
 
# Your last Question   

### Is there a difference between boys and girls with respect to belief in love at First sight?

$H_0$ : There is no difference between genders on belief in love at first sight.
$H_A$ : There is a difference between genders on belief in love at first sight.

```{r}
barchartGC(~sex + love_first,data=mydata)
```

There does not seem to be a difference with these bargrapghs. Both genders tend to have less belief in love at first sight.  

Numerical  

```{r}
table1 <- xtabs(~sex + love_first, data=mydata)
rowPerc(table1)
colPerc(table1)
```

In these tables, it tends to be more people do not believe in love at first sight, but in the second set, slightly more females believe in love at first sight.  

Inference  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The p-value of 1 means that we fail to reject the null hypo, so there must be a diffence between genders on belief of love at first sight.  

